Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-15 ind_files/05_unification_discussion.tex
Switch chap 5 and chap 6 epigraphs

\epigraph{\justifying Writing in the last months of this millenium, it is clear that the prime intellectual task of the future lies in constructing an appropriate theoretical framework for biology}{Sydney Brenner~\citep{brenner_theoretical_1999}}

>>>>

\epigraph{\justifying Not only is algebraic reasoning exact; it imposes an exactness on the verbal postulates made before algebra can start which is usually lacking in the first verbal formulations of scientific principles.}{J.B.S. Haldane~\citep{haldane_defense_1964}}

### 2023-03-15 ind_files/06_nontechnical_discussion.tex
Switch chap 5 and chap 6 epigraphs

\epigraph{\justifying Not only is algebraic reasoning exact; it imposes an exactness on the verbal postulates made before algebra can start which is usually lacking in the first verbal formulations of scientific principles.}{J.B.S. Haldane~\citep{haldane_defense_1964}}

>>>>

\epigraph{\justifying Writing in the last months of this millenium, it is clear that the prime intellectual task of the future lies in constructing an appropriate theoretical framework for biology}{Sydney Brenner~\citep{brenner_theoretical_1999}}
